%%********************************************************************
%% Appendix
%%*******************************************************
\chapter{Appendix}\label{chap:appendix}
These job postings were taken from the GitHub Jobs site. As they disappear
two weeks after their release, they are reprinted here for archiving.

\section{Job posting 1 - AeroTestra}\label{sec:job-posting-one}
%https://jobs.github.com/positions/efb0242c-1879-11e5-96f0-789c54126bcd
AeroTestra, Inc. is a startup and for-profit corporation that designs and
manufactures small Unmanned Aircraft Vehicles (sUAV ) located in San Carlos,
California. We are expanding operations to Mexico, Brazil, Chile and Japan over the
next couple of months using patent pending construction methods to develop and
manufacture sUAV that focus on functional solutions for organizations to quickly
and efficiently integrate sUAV into their workflow. Every part on our aircraft meets
the highest standards for reliable operation. We utilize a "thin shell structure" or
"exo-skeletal" airframe that is stiffer, lighter and stronger. It offers better protection for sensors, avionics and other sensitive electronics than conventional "skeletal" designs.\\

We are looking for an experienced software engineer to work in the ground up implementation of a data management system. You will be part of creating a system that
can efficiently transfer and store data, particularly images, for analysis in large volumes. The position entails working closely with the core team to implement functionality based on feedback from large commercial companies.

Requirements:
\begin{itemize}
\item Start Up Spirit and willingness to get your hands dirty
\item Work well in a team environment
\item BS or MS, Electrical or Computer Engineering preferred
\item Work independently without guidance and ability to drive own projects
\item Effectively communicate ideas in front of a group
\item Demonstrated leadership skills
\item Demonstrated experience working with server to server solutions
\item 2+ years experience in Python
\item Good knowledge of SQL (Oracle, MySQL, SQL Server) databases
\item Familiarity with UNIX/Linux environments
\item Experience in other languages such as Java or C++
\item Nice to haves:
\item Front-end web development experience
\item Familiarity with basic computer vision algorithms
\end{itemize}

Compensation: Substantial cash and/or equity compensation

\section{Job posting 2 - Must Win}\label{sec:job-posting-two}
% https://jobs.github.com/positions/24b8d828-1616-11e5-9bba-529723aeeb03
Must Win is a small team of goofballs who also happen to be all star software designers and developers. We're more than a dev shop. We work with our clients on a strategic level to help them realize their product vision. We've launched new businesses, helped companies pivot into new markets, accelerated product roadmaps, and consulted on technical problems that were impossible for in-house teams.\\

We were founded by seasoned Silicon Valley startup engineers who have created the kind of environment in which they always wanted to work. We've been around the block and pride ourselves on being the baddest, fastest, most fun, and highest quality dev shop in the business. We run a collaborative remote office with incredible work flexibility and amazing perks including 20 vacation days, two fully paid company trips to fun places like Costa Rica, a fully paid trip to the domestic conference of your choice (we'll also pay for any you speak at), and more!\\

THE ROLE: LEAD FULL-STACK DEVELOPER (leaning toward backend)\\

We're looking for an End-to-End engineer to lead teams of All Stars on client projects for some of the hottest brands in tech. If you're a star among stars and would enjoy the challenge of building new things every day then we want to talk to you!\\

\noindent WE'RE LOOKING FOR SOMEONE WITH:
\begin{itemize}
\item Experience providing strategic engineering solutions for difficult business objectives
\item A focus on the backend, but with the proficiencies to cover full-stack needs when need be
\item 3+ years of experience with back end development and architecture using modern web environments (like Ruby on Rails, GoLang, and/or Node.js), and common database needs (like Postgres \& Cassandra)
\item 3+ years of experience with JavaScript frameworks like AngularJS (our favorite these ways), Backbone, React, etc. Strong communication and project management skills
\end{itemize}

\section{Job posting 3 - Princeton University}\label{sec:job-posting-three}
% https://jobs.github.com/positions/3a2af518-1a96-11e5-97d7-c0ee0f353b80
The Department of Astrophysical Sciences at Princeton University has an open position for an experienced software developer to work on the development of the scientific data processing pipelines for the Large Synoptic Survey Telescope (LSST). The role will involve working with Jim Bosch \& John Swinbank within the Princeton Astronomical Data Group (led by Robert Lupton, Michael Strauss and Jim Gunn), which, in addition to LSST, is deeply involved in the Hyper Suprime Cam and Prime Focus Spectrograph instruments on the Subaru Telescope and expects to play a part in WFIRST, the space-based Wide Field Infrared Survey Telescope.\\

The LSST will conduct the largest astronomical survey yet undertaken, observing a total of 20000 square degrees in six bands and around 1000 epochs, collecting over 50 PB of raw data and measuring the properties of 40 billion astronomical sources. Princeton is responsible for multi-epoch deep imaging and catalog production based on the LSST survey. All software written for LSST will be made freely available under an open source license; all data collected made publicly available within the US with no proprietary period. This is a grant-funded, one-year term position with possibility of renewal.\\

\textit{Essential Qualifications}\\
We are seeking an experienced scientific software developer to contribute to the development of the scientific algorithms and supporting infrastructure. The ideal candidate would have at least 5 years of C++ expertise (required) and experience with collaborative software development in an astronomical environment (preferred). Knowledge of Python would be advantageous. An advanced degree in Physics, Astronomy, Computer Science or a related field, or equivalent practical experience is required.\\

We are seeking to recruit from as diverse a pool of talent as possible, and endeavor to preserve the Astrophysical Sciences Department's reputation as a pleasant workplace with a lively and friendly scientific atmosphere which recognizes that technical innovations are an important intellectual contribution to the science produced by major astronomical surveys.\\

Interested persons should send a curriculum vita including bibliography, if applicable, and provide contact information for three references. Letters of recommendation are encouraged.

\section{Job posting 4 - IBM}\label{sec:job-posting-four}
% https://jobs.github.com/positions/6107bb14-191d-11e5-9060-f0d7dcf002cf
Do you enjoy crafting beautiful and high performing web applications leveraging the latest front end development methodologies, tools, and techniques? Do you have an eye for design and a passion for delivering great user experiences?

At the nexus of engineering and design you will be instrumental in bringing industry-defining software products, cloud services and web applications to users around the world. You will play an integral role in building the next generation of advanced technologies in cloud, mobile, cognitive computing, big data, analytics and social software. If you're interested in making a global impact by delivering innovative user experiences - we want to hear from you!

Your responsibilities will include:
\begin{itemize}
\item Understanding user needs, and exploring user-centered designs
\item Specifying, building, testing, deploying, maintaining, and supporting your code
\item Leveraging modern tools and techniques to develop clean, efficient, and reusable code
\item Identifying and addressing design, development, and delivery performance bottlenecks
\item Actively participating in code and design reviews
\item Coaching, educating, and advocating front end development best practices
\end{itemize}

If you strive to be on a team that produces enterprise-grade code, is passionate about great design, and insists on delivering exceptional user experiences - this is the place for you! You should have a strong grasp of:

\begin{itemize}
\item Semantic HTML and modular CSS
\item JavaScript
\item Cross-browser quirks and compatibility
\item Mobile-first, content driven responsive design and development
\item Progressive enhancement
\item Leveraging APIs
\item Testing and resolving performance concerns
\item Team Git workflow and version control
\item Unix shell and command line tools
\end{itemize}

And earn bonus points if you're into:
\begin{itemize}
\item Visual or user experience design
\item Templating Languages (Handlebars.js, Dust.js, Swig, Jade, EJS)
\item CSS preprocessors (Sass, Less, Stylus)
\item JavaScript MVC frameworks (React, Backbone, AngularJS, Ember, etc)
\item Knowledge of emerging Web standards (Web Components, ECMAScript 6, HTTP/2, etc)
\item Native mobile development
\item Package managers (NPM, Bower, etc)
\item Scrum/agile software development methodologies
\item Building API driven interfaces
\end{itemize}

Minimum Requirements:
\begin{itemize}
\item 1+ years developing with HTML, CSS, JavaScript
\item 6+ months developing modular JavaScript
\item Fluent in English
\end{itemize}